---
title: "2024 Multi-Specialty Conference (2024MSC) Feedback Analysis Report"
output: html_document
execute: 
  echo: false
  warning: false
date-modified: 18 May 2024
---

<!-- This script does the following:

1. Reads the CSV file and splits the data into before and after 2024/05/11 based on the '_date' column.
2. Creates a pie chart showing the distribution of specialty categories among the speakers and participants.
3. Ranks the top 3 speakers based on the number of votes received in the feedback and creates a bar chart.
4. Creates a bar chart displaying the satisfaction levels from the feedback.
5. Displays a table listing the comments and commenter names from the feedback section.
-->



### Introduction
The 2024 Multi-Specialty Conference (2024MSC) brought together healthcare professionals from various specialties to discuss critical topics in public health. This report analyzes the feedback received from the conference participants and provides an overview of the event's success.


### Participant Demographics

<!--The pie chart illustrates the distribution of specialty categories among the speakers and participants.-->

```{r}
#| echo: false
library(tidyverse)
library(lubridate)
library(plotly)
library(knitr) # for light weight kable()
library(scales) # for percent()

# Read the CSV file
data <- read_csv("2024MSC_statistics_form.csv")

# Convert the '_date' column to datetime format
data$`_date` <- ymd_hms(data$`_date`)

# Split the data into before and after 2024/05/11
before_data <- data %>% dplyr::filter(`_date` < ymd("2024-05-11"))
after_data <- data %>% dplyr::filter(`_date` >= ymd("2024-05-11"))


####
# Count the number of participants by doctor/nurse/others category
category_counts <- before_data %>% 
  count(category) %>%
  mutate(percentage = n / sum(n) * 100)

# Create a pie chart of specialty categories
specialty_pie <- category_counts %>%
  plot_ly(labels = ~category, values = ~percentage, type = 'pie',
          textposition = 'inside',
          textinfo = 'label+percent',
          insidetextfont = list(color = '#FFFFFF'),
          hoverinfo = 'text',
          text = ~paste(category, ' (', n, ')'),
          marker = list(colors = colors,
                        line = list(color = '#FFFFFF', width = 1)),
          showlegend = FALSE,
          title = 'Participants Category Distribution') 
# %>%
#  layout(title = 'x Specialty Category Distribution')

specialty_pie

```
The conference attracted participants from diverse specialty backgrounds. The majority of the attendees were 48 doctors, followed by 23 nurses, and other healthcare professionals (4%). 
Total 15 speakers (including VIP remarks), and `r nrow(before_data) - 15` persons in audience registered online.


### Specialties of Speakers and Participants

<!-- Here's a script to generate descriptive statistics for the specialties of speakers and participants before 2024/05/11, along with an academic English description: -->

```{r}
# Read the CSV file
data <- read_csv("2024MSC_statistics_form.csv")

# Convert the '_date' column to datetime format
data$`_date` <- ymd_hms(data$`_date`)

# Filter data before 2024/05/11
before_data <- data %>% dplyr::filter(`_date` < ymd("2024-05-11"))

# Count the number of participants by specialty
specialty_counts <- before_data %>% 
  count(specialty, sort = TRUE)

# Display the specialty counts

knitr::kable(specialty_counts, align = 'l', row.names = FALSE)


# Orthopedics
# General Surgery
# Internal Medicine
```


The 2024 Multi-Specialty Conference (2024MSC) attracted a diverse range of healthcare professionals from various specialties. An analysis of the specialty distribution among speakers and participants who registered before 11 May, 2024, was conducted to gain insights into the conference's interdisciplinary nature.

The data revealed that the most well-represented specialty was **Orthopedics**, with `r specialty_counts$n[specialty_counts$specialty == "Orthopedics"]` individuals. This highlights the conference's strong focus on musculoskeletal health and related surgical interventions, such as **arthroscopic surgery in HGH**.

**General Surgery** followed closely, with `r specialty_counts$n[specialty_counts$specialty == "General Surgery"]` participants, reflecting the conference's emphasis on surgical disciplines, especially in minimal invasive **laparoscopic training centre in HGH**.

**Internal Medicine** had a notable presence, with `r specialty_counts$n[specialty_counts$specialty == "Internal Medicine"]` attendees, indicating the conference's attention to medical specialties dealing with the diagnosis, treatment, and prevention of adult diseases, such as noncommunicable diseases (NCDs) and **Dengue fever**.

Other specialties represented at the conference included Oral and Maxillofacial Surgery (OMS) (`r specialty_counts$n[specialty_counts$specialty == "OMS"]` participants), Radiology (`r specialty_counts$n[specialty_counts$specialty == "Radiology"]` participants), Pathology (`r specialty_counts$n[specialty_counts$specialty == "Pathology"]` participants), and one doctor working in tropical medicine. The presence of these specialties underscores the conference's commitment to fostering collaboration and knowledge exchange across various medical and surgical domains.

Interestingly, the data also revealed the participation of professionals from other essential areas of healthcare, such as Pharmacy (`r specialty_counts$n[specialty_counts$specialty == "Pharmacy"]` participants) and Nursing (`r specialty_counts$n[specialty_counts$specialty == "Cardiology"]` participants in Cardiology). This diversity in specialties emphasizes the conference's recognition of the interdisciplinary nature of healthcare and the importance of involving multiple disciplines in addressing complex medical challenges.

Furthermore, the conference attracted participants from specialties such as Neurology (`r specialty_counts$n[specialty_counts$specialty == "Neurology"]` participants), Nephrology (`r specialty_counts$n[specialty_counts$specialty == "Nephrology"]` participants), and Pediatrics (`r specialty_counts$n[specialty_counts$specialty == "Pediatrics"]` participants), showcasing the conference's comprehensive approach to healthcare across different age groups and organ systems.

In conclusion, the specialty distribution among speakers and participants at the 2024 **Multi-Specialty** Conference demonstrates the event's success in bringing together a wide array of healthcare professionals. The strong representation of Internal Medicine, General Surgery, and Orthopedics, along with the participation of various other medical and surgical specialties, highlights the conference's commitment to fostering interdisciplinary collaboration and knowledge sharing. This diversity in specialties positions the conference as a platform for addressing the complex and multifaceted challenges in healthcare, ultimately contributing to improved patient care and outcomes.


### Top Welcomed Speakers
Based on the feedback received, the top four speakers of the 2024MSC were:

1. Dr. Fadumo Ahmed Liban
2. Dr. Chin-I Chen
3. Dr. Abdilahi Abdi Ali
4. Dr. Jamal Tex LH Chi

These speakers were highly appreciated by the audience for their informative and engaging presentations. The bar chart visualizes the number of votes each top speaker received.


```{r}
####

# Count the number of votes for each speaker
speaker_counts <- after_data %>%
  count(speaker, sort = TRUE)

# Get the top 4 speakers
top_speakers <- speaker_counts %>%
  slice(1:4)

# Create a bar chart of the top 4 speakers
top_speakers_bar <- top_speakers %>%
  plot_ly(x = ~speaker, y = ~n, type = 'bar', 
          marker = list(color = 'blue'),
          hoverinfo = 'text',
          text = ~paste(speaker, ': ', n, ' votes')) %>%
  layout(title = 'Top 4 Best Speakers',
         xaxis = list(title = 'Speaker'),
         yaxis = list(title = 'Number of Votes'))

top_speakers_bar
```



### Satisfaction Levels
The conference received positive feedback from the participants regarding their overall satisfaction. 

The high percentage of "Very satisfied" and "Satisfied" responses indicates that the conference met the expectations of the majority of the attendees. The bar chart represents the satisfaction levels graphically.


```{r}
# Define the satisfaction levels in the desired order
satisfaction_levels <- c("Very satisfied", "Satisfied", "Neutral", "Dissatisfied", "Very dissatisfied")

# Count the number of responses for each satisfaction level
satisfaction_counts <- after_data %>%
  count(satisfaction)

# Add missing satisfaction levels with zero counts
missing_levels <- setdiff(satisfaction_levels, satisfaction_counts$satisfaction)
missing_data <- data.frame(satisfaction = missing_levels, n = 0)
satisfaction_counts <- bind_rows(satisfaction_counts, missing_data)

# Create a factor with the desired order of satisfaction levels
satisfaction_counts$satisfaction <- factor(satisfaction_counts$satisfaction, levels = satisfaction_levels)

# Define colors for each satisfaction level
colors <- c("darkgreen", "green", "yellow", "orange", "red")

# Create a bar chart of satisfaction levels
satisfaction_bar <- plot_ly(satisfaction_counts, x = ~satisfaction, y = ~n, type = 'bar',
                            marker = list(color = colors),
                            hoverinfo = 'text',
                            text = ~paste(satisfaction, ': ', n, ' responses')) %>%
  layout(title = 'Satisfaction Levels in 2024MSC',
         xaxis = list(title = paste('Satisfaction, n =', nrow(after_data)), categoryorder = "array", categoryarray = satisfaction_levels),
         yaxis = list(title = 'Number of Responses'))

satisfaction_bar

```

The satisfaction levels were as follows:

1. Very satisfied: `r percent(satisfaction_counts$n[satisfaction_counts$satisfaction == "Very satisfied"]/nrow(after_data))`
2. Satisfied: `r percent(satisfaction_counts$n[satisfaction_counts$satisfaction == "Satisfied"]/nrow(after_data))`
3. Neutral: `r percent(satisfaction_counts$n[satisfaction_counts$satisfaction == "Neutral"]/nrow(after_data))`


### Feedback and Comments
The participants provided valuable feedback and suggestions for future conferences. Some of the notable comments include:

1. "I am very thrilled the work that you done" - Dr. Abdirahman, HGH director
2. "Very good conference. Such conferences are much needed in Somaliland." - Dr. Hassan Nur
3. "Oncology department is missing from the HGH, which needs to be established." - Dr. Abdillahi Abdi Ali
4. "Topics should include research, articles, and cases done in hospitals of Somaliland." Dr. Nouh Ismail
5. "Please make this conference regular and invite those Doctors who always make positive change in their community and those who always make a research and are going to publish studies by sharing their knowledge with others." - Dr. Faadumo


The comments highlight the importance of the conference in addressing healthcare issues in Somaliland and suggest areas for improvement, such as including more research-based presentations and establishing an oncology department at the Hargeisa Group Hospital.

The other comments:
```{r}
# Create a table of comments and commenter names
comments_table <- after_data %>%
  select(name, comments) %>%
  dplyr::filter(!is.na(comments) & comments != "") %>%
  rename(`Commenter Name` = name, `Comment` = comments)

# Display the table
knitr::kable(comments_table, align = 'l', row.names = FALSE)

```

### Conclusion
The 2024 Multi-Specialty Conference successfully brought together healthcare professionals from various specialties to discuss important public health topics. The positive feedback received from the participants demonstrates the conference's impact and the need for similar events in the future. The organizing committee will take the feedback and suggestions into consideration to improve the upcoming conferences and continue to contribute to the advancement of healthcare in Somaliland.


We wish see you soon on 2025MSC in Somaliland!

In sha Allah,  إن شاء الله
